Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (1)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{resposta} 
We thank the reviewer fot this insightful comment. Indeed, it summarizes what was intended to be studied in this manuscript. Additionally, we emphasize that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modelling, which was already investigated by prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction and conclusion sections since we concluded that it was unclear in the previous version of our manuscript. Regarding Figure 2, we fixed it as indicated by the reviewer. Moreover, we applied the same procedure to voltage V, in order to keep consistency throughout our manuscript.

>>>>

\begin{resposta} 
We thank the reviewer fot this insightful comment. Indeed, it summarizes what was intended to be studied in this manuscript. Additionally, we have emphasized that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modelling, which was already investigated in prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript. Regarding Figure 2, we fixed it as recommended by the reviewer. Moreover, we applied the same procedure to voltage V, in order to keep consistency throughout our manuscript.
